---
title: "Iteration and Listcols"
author: "ak5357"
date: "2024-10-29"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```



## Here's some lists
```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)
```

```{r}
l$mat

l[["mat"]][1, 3]

l[[1]]
l[[4]]
```


Make a list that's hopefully more useful

Use Ctrl+alt+arrow to type in multiple rows at the same time. Can use ctrl+shift+alt to select multiple rows at a time. Some combination of these also

* switch rows
* duplicate rows

```{r}
list_norm =
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```


Reusing function from last class.

```{r}
mean_and_sd = function(x){
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = tibble(
    mean = mean_x,
    sd = sd_x
  )
  
  return(out_df)
}
```

Let's use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

# Use a for loop

Create output list and run a for loop.
```{r}
# creating empty list with 4 spots
output = vector("list", length = 4)

for(i in 1:4){
  output[[i]] = mean_and_sd(list_norm[[i]])
}

output
```










