---
title: "Iteration and Listcols"
author: "ak5357"
date: "2024-10-29"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```



## Here's some lists
```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)
```

```{r}
l$mat

l[["mat"]][1, 3]

l[[1]]
l[[4]]
```


Make a list that's hopefully more useful

Use Ctrl+alt+arrow to type in multiple rows at the same time. Can use ctrl+shift+alt to select multiple rows at a time. Some combination of these also

* switch rows
* duplicate rows

```{r}
list_norm =
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```


Reusing function from last class.

```{r}
mean_and_sd = function(x){
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = tibble(
    mean = mean_x,
    sd = sd_x
  )
  
  return(out_df)
}
```

Let's use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

# Use a for loop

Create output list and run a for loop.
```{r}
# creating empty list with 4 spots
output = vector("list", length = 4)

for(i in 1:4){
  output[[i]] = mean_and_sd(list_norm[[i]])
}

output
```

## Do the same thing

but with `map` instead

```{r}
output = map(list_norm, mean_and_sd)
```

Change output to dataframe

```{r}
output = map(list_norm, mean_and_sd) |> 
  bind_rows()

output = map_dfr(list_norm, mean_and_sd)

output = map_dbl(list_norm, mean_and_sd)


```

## List Columns

```{r}
listcol_df =
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm #must be same number of things in col 1 and col 2
  )

listcol_df

listcol_df |> 
  filter(name %in% c("a", "b"))

listcol_df |> 
  select(-samp)
```

```{r}
listcol_df[["samp"]][["a"]]
```

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

map_dfr(listcol_df[["samp"]], mean_and_sd)
```


Add a list column
```{r}
listcol_df |> 
  mutate(
    iqr = map_dbl(samp, IQR),
    # mean = map_dbl(listcol_df[["samp"]], mean),
    # sd = map_dbl(listcol_df[["samp"]], sd),
    output = map(listcol_df[["samp"]], mean_and_sd)
  ) |> 
  select(-samp) |> 
  unnest(output)

```

Revisiting NSDUH
```{r}
nsduh_table <- function(html, table_num) {
  
  out_table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(out_table)
}
```

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
nsduh_html = read_html(nsduh_url)
```


```{r}
nsduh_table(nsduh_html, 1)
nsduh_table(nsduh_html, 4)
nsduh_table(nsduh_html, 5)
```

```{r}

output = vector("list", 3)

for (i in c(1, 4, 5)) {
  output[[i]] = nsduh_table(nsduh_html, i)
}

nsduh_results = bind_rows(output)
```

```{r}
map(c(1, 4, 5), nsduh_table, html = nsduh_html)
```


```{r}
nsduh_df = 
  tibble(
    drug = c("marj", "cocaine", "heroin"),
    table_n = c(1, 4,5 )
  ) |> 
  mutate(table = map(table_n, nsduh_table, html = nsduh_html)) |> 
  unnest(table)

nsduh_df |> 
  filter(drug == "New York") |> 
  pivot_longer(
    cols = -c(drug, table_n, State),
    names_to = "date",
    values_to = "pct_usage"
  )

nsduh_df |> 
  tibble(
    drug = c("marj", "cocaine", "heroin"),
    table_n = c(1, 4, 5)
  ) |> 
  mutate(
    table = map(table_n, \(x) nsduh_table)
  )
```


Weather example
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USW00022534 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Create a list column.

```{r}
weather_nest = 
  weather_df |> 
  nest(data = date:tmin)
```

```{r}
weather_nest[["data"]][[1]]
```

Let's try regressing tmax on tmin.
```{r}
lm(tmax ~ tmin, data = weather_nest[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[3]])
```

OR

```{r}
weather_nest |> 
  mutate(model_fit = map(data, \(x) lm(tmax ~ tmin, data = x))) |> 
  pull(model_fit)
```













