---
title: "Writing Functions"
author: "ak5357"
date: "2024-11-12"
output: github_document
---

Load key packages.
```{r setup_libraries, include = FALSE}
library(tidyverse)
library(readxl)
library(rvest)
library(ggplot2)
```

```{r setup_theme}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(
  theme_minimal()+
  theme(legend.position = "bottom")  
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Writing my first function!!

As an example, here's a z-score computation.
```{r}
x_vec = rnorm(n = 25, mean = 10, sd = 3.5)

# z-score computation
(x_vec - mean(x_vec)) / sd(x_vec)
```

Now I'll write a function to do this.
```{r}
# Define the function
z_scores = function(x){
  z = (x - mean(x)) / sd(x)
  return(z)
}
```

```{r}
# Call the function
z_scores(x = x_vec)
```

Does this always work?
```{r, error = TRUE}
# Cases where it doesn't work
z_scores(x = 3)
z_scores(x = c("my", "name", "is", "arghya"))
```

```{r, error = TRUE}
# Add checks into the function
z_scores = function(x){
  # Conditional execution --> check whether it'll break the function
  if(!is.numeric(x)){
    stop("x needs to be numeric")
  } else if (length(x) < 5){
    stop("you need at least 5 numbers to compute the z-score")
  }
  
  # Create and return output
  z = (x - mean(x)) / sd(x)
  return(z)
}
```

Check again.
```{r, error = TRUE}
# Cases where it doesn't work
z_scores(x = 3)
z_scores(x = c("my", "name", "is", "arghya"))
```

## A new function!

```{r}
mean_and_sd = function(x){
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
}
```

```{r}
mean_and_sd(x_vec)
```

## Check stuff using a simulation

```{r}
sim_df =
  tibble(
    x = rnorm(30, 10, 5)
  )

sim_df |> 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```


Simulation function to check sample mean and sd.

```{r}
sim_mean_sd = function(samp_size, true_mean = 10, true_sd = 5){
  sim_df =
    tibble(
      x = rnorm(samp_size, true_mean, true_sd)
    )
  
  out_df =
    sim_df |> 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
  
  return(out_df)
  
}

# can play around with this to see if the central limit theorem actually works
sim_mean_sd(30, 10, 5)
sim_mean_sd(30, 4, 12)
sim_mean_sd(3000, 4, 0.12)

# after adding default values
sim_mean_sd(3000)

# can enter arguments out-of-order ONLY IF NAMED
sim_mean_sd(true_sd = 5, samp_size = 3000)
```

## Revisit LoTR words

```{r}
fellowship_df =
  read_excel("data/LotR_Words.xlsx", range = "B3:D6") |> 
  mutate(movie = "fellowship") |> 
  janitor::clean_names()

two_towers_df =
  read_excel("data/LotR_Words.xlsx", range = "F3:H6") |> 
  mutate(movie = "two_towers") |> 
  janitor::clean_names()

return_king_df =
  read_excel("data/LotR_Words.xlsx", range = "J3:L6") |> 
  mutate(movie = "return_king") |> 
  janitor::clean_names()
```

Learning assessment: Import LoTR tables
```{r}
get_lotr_table = function(file_path = "data/LotR_Words.xlsx", movie_name, cell_range){
  out_df =
    read_excel(file_path, range = cell_range) |> 
    mutate(movie = movie_name) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |> 
    relocate(movie)
  
  return(out_df)
}

lotr_df =
  bind_rows(
    get_lotr_table(movie_name = "fellowship", cell_range = "B3:D6"),
    get_lotr_table(movie_name = "two_towers", cell_range = "F3:H6"),
    get_lotr_table(movie_name = "return_king", cell_range = "J3:L6")
  )
```


## NSDUH

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

marj_table = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  mutate(drug = "marijuana")

cocaine_table = 
  nsduh_html |> 
  html_table() |> 
  nth(4) |>
  slice(-1) |> 
  mutate(drug = "marijuana")

heroin_table = 
  nsduh_html |> 
  html_table() |> 
  nth(5) |>
  slice(-1) |> 
  mutate(drug = "marijuana")
```

Learning assessment: Import NSDUH tables
```{r}

nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
nsduh_html = read_html(nsduh_url)

nsduh_import = function(drug_name, table_n, html){
  out_table =
    html |> 
    html_table() |> 
    nth(table_n) |> 
    slice(-1) |>
    mutate(drug = drug_name) |> 
    relocate(drug) |> 
    select(-contains("P Value"))
  
  return(out_table)
}

bind_rows(
  nsduh_import("marijuana", 1, nsduh_html),
  nsduh_import("cocaine", 4, nsduh_html),
  nsduh_import("heroin", 5, nsduh_html)
  )
```


Pull function from separate R file.

```{r}
source("source/nsduh_import.R")

bind_rows(
  nsduh_import("marijuana", 1, nsduh_html),
  nsduh_import("cocaine", 4, nsduh_html),
  nsduh_import("heroin", 5, nsduh_html)
  )
```







